---
title: 'tidycovid19 패키지에 대해 알아보자.'
author: 최의용
date: '2020-06-10'
slug: 'tidycovid19 패키지에 대해 알아보자.'
categories:
  - R
tags:
  - 미완성의신
  - R
  - tidyverse
  - tidycovid19
  - covid19
  - corona
---

2020년 지금 우리는 코로나의 시대에 노출되어 있다. 가볍게 지나갈것 같았던 코로나는 약 7개월동안, 그리고 앞으로 언제까지도 지속될지 이제는 모르는 상황이다. R공부를 하면서 Tidyverse를 알게 되었고, Covid19에 대해 찾아 보다가 다음의 패키지를 알게 되었다. `tidycovid19`라는 패키지인데, 찾아 보니 많은 데이터를 넣어서 잘 만들어 좋은 패키지라 본다. joachim-gassen이라는 사람이 만든 패키지로 이분은 이 패키지를 다음과 같이 이름을 지었다.


>> Download, Tidy and Visualize Covid-19 Related Data

깃헙 링크를 보면 더 자세하게 알수 있으며 이번 블로그는 깃헙에 적인 내용을 정리해보는 시간을 가져보려 한다.

- Github: [joachim-gassen/tidycovid19](https://github.com/joachim-gassen/tidycovid19)
- 블로그 링크(같은 내용이지만 더 잘 되어 있음): [tidycovid19](https://joachim-gassen.github.io/tidycovid19/index.html)

# 다른 Covid-19 R packages는?

- {nCov2019}: 이 패키지는 중국 데이터에 중점울 두었지만 중국을 외에도 다른 나라 데이터를 포함하고 있다.
- {coronavirus}: 이 패키지는 대시보드와 함께 Johns Hopkins University CSSE dataset를 제공한다.

또한, 추가적으로 관련 자료 링크 두가지를 소개 해주는데, 이 두개만 해도 많은 자료를 담고 있다.

- Stats and R: [Top 100 R resources on Novel COVID-19 Coronavirus](https://www.statsandr.com/blog/top-r-resources-on-covid-19-coronavirus/)

- github 링크: [mine-cetinkaya-rundel/covid19-r](https://github.com/mine-cetinkaya-rundel/covid19-r)


# Data 

현재 이 패키지는 다음의 함수를 통해 데이터를 제공한다.

  - `download_jhu_csse_covid19_data()`: 이 데이터는 바이러스의 전지구적 확산을 평가하는 데 관심이 있는 연구자와 일반 청중을 위한 표준 자료로 발전했다. 데이터는 국가 및 하위 국가 수준에서 제공된다.
    - 다운로드 링크: [Covid-19 data from the Johns Hopkins University CSSE Github Repo](https://github.com/CSSEGISandData/COVID-19). 
  - `download_ecdc_covid19_data()`: 이 데이터는 매일 업데이트 되고, 일별 및 국가별로 Covid-19의 사례에 대한 최신 데이터가 포함되어 있다.
    - 다운로드 링크: [Covid-19 case data provided by the European Centre for Disease Prevention and Control](https://www.ecdc.europa.eu/en/publications-data/download-todays-data-geographic-distribution-covid-19-cases-worldwide). 
  - `download_owid_testing_data()`: This team systematically collects data on Covid-19 testing from multiple national sources.
    - 다운로드 링크: [testing data collected by the ‘Our World in Data’ team](https://ourworldindata.org/covid-testing). 
  - `download_acaps_npi_data()`: Downloads and tidies the [Government measures dataset provided by the Assessment Capacities Project (ACAPS)](https://www.acaps.org/covid19-government-measures-dataset). These data allow researchers to study the effect of non-pharmaceutical interventions on the development of the virus. 
  - `download_oxford_npi_data()`: Downloads and tidies data from the [Oxford Covid-19 Government Response Tracker](https://www.bsg.ox.ac.uk/research/research-projects/oxford-covid-19-government-response-tracker), an alternative data source for governmental interventions. Currently, I do not include the financial measures of this data set and also do not include its data in the merged data file (see below) as I view the ACAPS data to be better suited ([this blog post details why](https://joachim-gassen.github.io/2020/04/exploring-and-benchmarking-oxford-government-response-data/)).
  - `download_apple_mtr_data()`: Downloads [Mobility Trends Reports provided by Apple](https://www.apple.com/covid19/mobility) related to Covid-19. The data is provided at country and sub-country levels.
  - `download_google_cmr_data()`: Downloads [Google COVID-19 Community Mobility Reports](https://www.google.com/covid19/mobility/) data. As of April 17, Google provides a nice and clean CSV file containing country-day and region-day data. This makes the PDF scraping code that used to be part of this package obsolete. If you are interested in it for didactic reasons, you can still find it in the [git hstory](https://github.com/joachim-gassen/tidycovid19/tree/947f010bccb111bc181ca31889c6f2f86b841fb5/R). This data is available at the country, regional and U.S. county level.
  - `download_google_trends_data()`: Downloads and tidies [Google Trends](https://trends.google.com/trends/) data on the search volume for the term “coronavirus” (Thank you to Yan Ouaknine for bringing up that idea\!). This data can be used to assess the public attention to Covid-19 across countries and over time within a given country. The data is available at the country, regional and city level but availability varies across countries as Google Trends provides only more granular data for regions with high search volumes.
  - `download_wbank_data()`: Downloads and tidies additional country level information provided by the [World Bank](https://data.worldbank.org) using the {wbstats} package. These data allow researchers to calculate per capita measures of the virus spread and to assess the association of macro-economic variables with the development of the virus.
  - `download_merged_data()`: Downloads all data sources and creates a merged country-day panel.




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

```{r}
library(tidyverse)
library(tidycovid19)
library(zoo)
library(knitr)
```


```{r}
df <- download_merged_data(cached = TRUE, silent = TRUE)
```



# Referenct 

- https://github.com/joachim-gassen/tidycovid19/blob/master/README.md

- https://accounting-for-transparency.de/

- https://joachim-gassen.github.io/2020/04/covid19-explore-your-visualier-dof/

- https://joachim-gassen.github.io/2020/04/exploring-and-benchmarking-oxford-government-response-data/

- https://joachim-gassen.github.io/2020/03/merge-covid-19-data-with-governmental-interventions-data/

- https://joachim-gassen.github.io/2020/03/meet-tidycovid19-yet-another-covid-19-related-r-package/

- https://joachim-gassen.github.io/2020/05/tidycovid19-new-data-and-doc/
